The Iterative Signature Algorithm

### 2009-04-01 isa/inst/doc/ISA_tutorial.Rnw
Added references to isa vignette.

@@

>>>>

TODO

@@

\bibliographystyle{apalike}

\begin{thebibliography}{}

\bibitem[Bergmann et~al., 2003]{isa}
Bergmann, S., Ihmels, J., and Barkai, N. (2003).
\newblock Iterative signature algorithm for the analysis of large-scale gene
  expression data.
\newblock {\em Phys Rev E Nonlin Soft Matter Phys}, page 031902.

\bibitem[Cs\'ardi, 2009]{isapackage}
Cs\'ardi, G. (Apr 1, 2009).
\newblock {\em isa: The Iterative Signature Algorithm}.
\newblock R package version 0.1.

\bibitem[Ihmels, 2002]{sa}
Ihmels, J., Friedlander, G., Bergmann, S., Sarig, O., Ziv, Y., 
Barkai, N. (2002).
\newblock Revealing modular organization in the yeast transcriptional
  network.
\newblock { \em Nat Genet }, page 370--7.

\bibitem[Ihmels, 2004]{isamod}
Ihmels, J., Bergmann, S., Barkai, N. (2004).
\newblock Defining transcription modules using large-scale gene
  expression data.
\newblock { \em Bioinformatics}, page 1993--2003.

\end{thebibliography}
